---
title: "Appendix 12 - more supplementary protocol and writeups, or something"
subtitle: "\"A very long subtitle\""
author: "Darach Miller, etc."
date: "2018"
toc: True
fontsize: "12pt"
mainfont: DejaVuSans
output:
  pdf_document:
    fig_width: 5
    fig_height: 3
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
    latex_engine: xelatex
# This uses the awesome answer here ( https://stackoverflow.com/a/33801326 ) to make it work!!!
---

# Introduction

Whereas `rmarkdown` is a package that knits using `knitr`, then uses
`pandoc` to typeset PDFs, sometimes you want to have your figures
handle a bit different.

## Some numbers

Maybe you want some bunch of numbers[^whatevz].

```{r, making_numbers_in_secret, echo=F, cache=T, fig.cap="Making some numbers and plotting."}
prot_datar <- rpois(1e4)^10
mrna_datar <- rpois(1e4)^2

hist(mrna_datar,breaks=100)
hist(prot_datar,breaks=100)
```

[^whatevz]: or whatever

## Other numbers

Maybe 2$\mu$L of those, scd6$\Delta$.

Action | Treatment series | Minutes after uracil chase
---|---|---
+4.5ml 400mM uracil | water (mock upshift) |  0
Took sample 1 | water |  3.85
Took sample 2 | water |  6.02

```{r, modeling_in_secret, echo=F, cache=T, fig.cap="Residual whatever, but with a magic \\LaTeX label right here. \\label{fig:normgenes}"}

plot(mrna_datar,prot_datar,type="l")

#theResiduals <- pdat %>% filter(Variable=="residuals")%>%
#  ggplot()+aes(x=expmin,y=Value,col=treatment)+theme_bw()+
#  geom_point()+geom_rug(sides="r")+ 
#  xlab("Minutes after chase")+
#  ylab("Residuals from that fit")
#theResiduals
```

We did an ANCOVA (`aov`/`lm`), and found the effect of treatment
was associated with a p-value $<$ `r c(z[[1]])[[5]][[2]]` and
the p-value associated with time estimated as "1",
so it does not appear that the residuals depend on time or
treatment. 

`r signif(c(zeroMod[3])/c(zeroMod[2])*100,3)`% increase in the rate.

How do the normalizations compare on a per-gene basis? 
Figure \ref{fig:normgenes} shows the normalized data for several genes,
on the left is the direct, within sample normalization 
and on the right is this smoothing between samples using a 
log-linear model.

What does this mean for our estimates of destabilization?
What effect sizes are estimated, and how do they compare to this
inflation of `r signif(c(zeroMod[3])/c(zeroMod[2])*100,3)`%? 
Figure \ref{fig:changeRateDist} shows the distribution of the fold changes in stability:


