---
title: "Appendix 12 - more supplementary protocol and writeups, or something"
subtitle: "\"A very long subtitle\""
author: "Darach Miller, etc."
date: "2018"
toc: True
fontsize: "12pt"
mainfont: DejaVuSans
output:
  rmarkdown::pdf_document:
    fig_width: 5
    fig_height: 3
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
    latex_engine: xelatex
# This uses the awesome answer here ( https://stackoverflow.com/a/33801326 ) to make it work!!!
---

```{r,libraries,echo=F,warning=F,error=F}
library(ggplot2)
```

# Introduction

It might be nice to customize this a bit, so you can use rmarkdown
documents to direct output out as supplementary files, PDFs for 
publication.
Whereas `rmarkdown` is a package that knits using `knitr`, then uses
`pandoc` to typeset PDFs, you're going to have to use a few
\LaTeX\space tricks to make this work.

For example, figures with float all
over the place. Which is cool, but maybe you want your figures 
exactly where they appear in the text, sorta, and are willing to
tolerate whitespace to get them there. By using the 
`preamble=latex.tex` in the YAML header, you can get around this.

## Some numbers

Maybe you want some bunch of numbers[^whatevz] with a footnote. 
Make them in un-echoed chunks. 

```{r, making_numbers_in_secret, echo=F, cache=T}
datar <- data.frame(
  prot=rnorm(1e4,mean=100)^2,
  mrna=rnorm(1e4,mean=10)^2
  )
```

Then do plots one at a time. Make sure you're just outputting one
plot, one per chunk and per `fig.cap`.

```{r, plotting_both, depends.on="making_numbers_in_secret", echo=F, cache=T, fig.cap="both"}
ggplot(datar)+aes(x=mrna)+geom_histogram(bins=50)
ggplot(datar)+aes(x=prot)+geom_histogram(bins=50)
```

Both will scramble the caption, so instead do one output plot per chunk.

```{r, plotting_one, depends.on="making_numbers_in_secret", echo=F, cache=T, fig.cap="One.  \\label{fig:earlier}"}
ggplot(datar)+aes(x=mrna)+geom_histogram(bins=50)
```

```{r, plotting_other, depends.on="making_numbers_in_secret", echo=F, cache=T, fig.cap="Other"}
ggplot(datar)+aes(x=prot)+geom_histogram(bins=50)
```

Or use something like `cowplot`, then you can use letter refs in 
the caption.

```{r, plotting_both_for_real, depends.on="making_numbers_in_secret", echo=F, cache=T, fig.cap="both A and B are there"}
cowplot::plot_grid(ggplot(datar)+aes(x=mrna)+geom_histogram(bins=50),
  ggplot(datar)+aes(x=prot)+geom_histogram(bins=50),
  labels=c("A","B"),ncol=2)
```

[^whatevz]: or whatever

## Other numbers

Maybe 2$\mu$L of those, scd6$\Delta$. $$\text{Math} = a*x + b $$.
Here's a table.

Action | Treatment series | Minutes after uracil chase
---|---|---
+4.5ml 400mM uracil | water (mock upshift) |  0
Took sample 1 | water |  3.85
Took sample 2 | water |  6.02

Also, let's say you want to make it wider.

```{r, modeling_in_secret, depends.on="making_numbers_in_secret", echo=F, cache=T, fig.cap="Residual whatever, but with a magic \\LaTeX\\space labeling right here. \\label{fig:normgenes}",fig.width=8}
g1 <- ggplot(datar)+aes(x=mrna,y=prot)+geom_point()

some_model <- lm(data=datar, log(prot)~log(mrna) )
f <- function(x,this_model=some_model) { exp(log(x)*coef(this_model)[2]+coef(this_model)[1]) }
g2 <- g1+stat_function(fun=f,col="red")

cowplot::plot_grid(g1,g2,labels=c("A","B"),ncol=2)
```

or taller

```{r, this_is_taller, depends.on="making_numbers_in_secret", echo=F, cache=T, fig.cap="Taller.",fig.height=6}

cowplot::plot_grid(g1,g2,labels=c("A","B"),ncol=2)
```

You can do that with the `fig.width` or `fig.height` options.

Note in this text, you can also add custom dependencies like with
`depends.on` so that changing an earlier will re-run everything
that depends on it.

You can access the variables in-line of the text, so you can say
the model had a slope with a p-value of $<$ 
`r summary(some_model)$coefficients[2,4]` or 
`r signif(summary(some_model)$coefficients[2,4],3)`.
.

Figure \ref{fig:normgenes} shows that you can ref figures,
or other ones like number \ref{fig:earlier}.
Click on them. They're hyperlinks.

